Draft2

### 2022-04-20 Draft2.Rmd
the sorting part got tricky. might have to separate the air pollutant types, save them into diff objects, and then mutate for them all to be in one table??

```{r}

@@

```{r}

@@

```{r}

>>>>

```{r}
glimpse(deaths_df)

#This is the average of all countries by type of air pollutant death
deaths_df %>% 
  group_by(country) %>% 
  select(indoor_deaths, outdoor_deaths, ozone_deaths) %>% 
  summarize(avg_indoor = mean(indoor_deaths), avg_outdoor = mean(outdoor_deaths), avg_ozone = mean(ozone_deaths))

#Sort descending to see which country had the highest of each...(not sure if this is right)
#does separating the arrange individually fix it??
deaths_df %>% 
  group_by(country) %>% 
  select(indoor_deaths, outdoor_deaths, ozone_deaths) %>% 
  summarize(avg_indoor = mean(indoor_deaths), avg_outdoor = mean(outdoor_deaths), avg_ozone = mean(ozone_deaths)) %>% 
  arrange(desc(avg_indoor), desc(avg_outdoor), desc(avg_ozone))
```

@@

```{r}
deaths_df %>% 
  group_by(country, year) %>% 
  summarize(avg_indoor = mean(indoor_deaths), avg_outdoor = mean(outdoor_deaths), avg_ozone = mean(ozone_deaths)) %>% 
  arrange(desc(avg_indoor)) %>% 
  arrange(desc(avg_outdoor)) %>% 
  arrange(desc(avg_ozone))
````

@@

```{r}
#Probably need to fix the above to answer this one
